---
title: "Lab7"
author: "Mariama Jaiteh"
date: "2/27/2017"
output: html_document
---
<h1>Working with Tidy in R </h1>

When you have same data and want to clean it up.Tidy data are usually long and narrow. That is, it may have many rows, but relatively few columns. However, data are often stored in spreadsheets in a wide format, which may have more columns that rows. I believe this is because the wide format is easier to see in a spreadsheet. However, it turns out that there are lots of good reasons to keep data in a tidy format.
```{r}
library(tidyverse)
library(babynames)


```
The gather() and spread() functions from the tidyr package (written by guess who?) are huge time-savers. I don’t know of any equivalent operation in Excel that can do what these functions do. In short, gather() takes a data table in a wide format and converts it into a tidy format. spread() does the opposite (and accordingly, is used less frequently).

```{r}
ssa_births <- babynames %>%
  group_by(year) %>%
  summarize(N = n(), births = sum(n))
total_births <- births %>%
  left_join(ssa_births, by = "year")
head(total_births)


```

```{r}
 total_births <- total_births %>%
  select(-N) %>%
  rename(census = births.x, ssa = births.y)
```
Each row corresponds to a single year, and for each year, we have two variables: census (from the Census) and ssa (from the SSA). This data frame is not tidy.(Why?)
When we graph them, we are forced to use a second y aesthetic instead of a direct mapping.
```{r}
ggplot(data = total_births, aes(x = year, y = census)) +
  geom_line() + 
  geom_line(aes(y = ssa))
```

```{r}
dim(total_births)
```
```{r}
births_tidy <- total_births %>%
  gather(key = "source", value = "births", -year)
head(births_tidy)
dim(births_tidy)

```

